---
title: "Workflows and Included Examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Workflows and Included Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package ships with concrete example apps and fixtures that exercise the analysis pipeline.

## Example apps

### `examples/basic_app`

This is the happy-path example. It includes:

- `reactive()`
- `eventReactive()`
- `observeEvent()`
- `observe()`
- `reactiveVal()`
- `reactiveValues()`
- `renderText()`
- `renderTable()`
- `renderPlot()`
- sourced helper functions
- side-effect calls such as `write.csv()` and `message()`

```{r}
library(shinybrain)

basic_app <- system.file("examples", "basic_app", package = "shinybrain")
if (basic_app == "") basic_app <- file.path("inst", "examples", "basic_app")
if (!dir.exists(basic_app)) basic_app <- file.path("examples", "basic_app")

basic_result <- analyze_shiny_project(basic_app)
table(basic_result$contexts$context_type)
```

### `examples/edge_case_app`

This app is designed for analyzer edge cases rather than runtime execution. It includes:

- a resolved `source("helpers.R")`
- a missing source target
- a dynamic `source()` call
- a dynamic `input[[...]]` lookup

```{r}
edge_app <- system.file("examples", "edge_case_app", package = "shinybrain")
if (edge_app == "") edge_app <- file.path("inst", "examples", "edge_case_app")
if (!dir.exists(edge_app)) edge_app <- file.path("examples", "edge_case_app")

edge_result <- analyze_shiny_project(edge_app)
edge_result$issues[, c("severity", "issue_type")]
```

## Fixture-level workflows

The `tests/fixtures/` directory contains small focused projects for regression testing:

- `basic_single_file`
- `observer_and_state`
- `source_chain`

These are useful when you want compact reproducible inputs while working on the parser or graph builder.

## Export workflow

Once you have a `brain` object, the usual downstream workflow is:

```r
brain <- build_brain(basic_result)

export_brain_json(brain, "brain.json")
export_brain_markdown(brain, "brain.md")
export_brain_html(brain, "brain.html", open = FALSE)
```

## Smoke-test runner

The repository includes a convenience runner:

```r
source("examples/run_example.R")
```

It analyzes the bundled example apps, prints summaries, and writes export artifacts to a temporary directory.
