---
title: "Getting Started with shinybrain"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with shinybrain}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`shinybrain` statically analyzes Shiny application source code and turns it into a portable "App Brain" object. This vignette walks through the smallest useful workflow.

## Analyze a project

```{r}
library(shinybrain)

app_dir <- system.file("examples", "basic_app", package = "shinybrain")
if (app_dir == "") app_dir <- file.path("inst", "examples", "basic_app")
if (!dir.exists(app_dir)) app_dir <- file.path("examples", "basic_app")

result <- analyze_shiny_project(app_dir)
names(result)
```

The analysis result contains project metadata plus the internal tibbles used by the parser and graph builder:

- `project`
- `files`
- `contexts`
- `symbols`
- `references`
- `nodes`
- `edges`
- `issues`

## Build an App Brain

```{r}
brain <- build_brain(result)
brain$summary
```

The App Brain is the package's portable reporting object. It includes:

- project metadata
- file inventory
- graph nodes and edges
- generated insights
- issue records
- export options

## Print a console summary

```{r}
print_brain_console(brain)
```

## Export for downstream use

```r
export_brain_json(brain, "brain.json")
export_brain_markdown(brain, "brain.md")
export_brain_html(brain, "brain.html", open = FALSE)
```

## Single-file apps

If you already know the app entry file, use `analyze_shiny_file()`:

```{r}
single_file <- file.path(app_dir, "app.R")

single_result <- analyze_shiny_file(single_file)
nrow(single_result$contexts)
```

## Next steps

See `vignette("shinybrain-workflows")` for a tour of the included example apps and typical analysis workflows.
